On change of priors in one-vs-one classification methods

### 2025-05-13 coupling.tex
Explanation remark in the caption of summary table

\begin{table}[!ht]
\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
\hline 
\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
&uniqueness &  yes & yes & yes & yes & yes & yes \\
&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
&canonicity & yes & no & yes & yes & no & yes \\
&symmetry & yes & yes & yes & yes & no & yes \\
& Bayes covariant & no & no & no & yes & yes & yes \\
\hline
\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
&lack of parameters & yes & yes & yes & yes & yes & yes \\
& amounts to a linear system & no & yes & yes & yes & yes & yes\\
& linear system of special form & N/A & no & yes & yes & yes & yes \\
& iterative method & yes & yes & yes & no & not needed & not needed\\
\hline
\end{tabular}
\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
\label{tab:summaryCoupling}
\end{table}

>>>>

\begin{table}[!ht]
\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
\hline 
\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
&uniqueness &  yes & yes & yes & yes & yes & yes \\
&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
&canonicity & yes & no & yes & yes & no & yes \\
&symmetry & yes & yes & yes & yes & no & yes \\
& Bayes covariant & no & no & no & yes & yes & yes \\
\hline
\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
&lack of parameters & yes & yes & yes & yes & yes & yes \\
& amounts to a linear system & no & yes & yes & yes & yes & yes\\
& linear system of special form & N/A & no & yes & yes & yes & yes \\
& iterative method & yes & yes & yes & no & not needed & not needed\\
\hline
\end{tabular}
\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}. The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng [\cite{wu2004probability}].}
\label{tab:summaryCoupling}
\end{table}
